%_____________________________________________________________________________________________ 
% LATEX Template: Department of Comp/IT BTech Project Reports
% Abstract of Report
% Sun Mar 27 10:34:00 IST 2011
%_____________________________________________________________________________________________ 

\begin{abstract}
%\addcontentsline{toc}{chapter}{Abstract}	% This makes sure abstract is included in contents.
There are a wide range of users in the computer world. Computer users may or may not be well versed in English language. So there is need to make available software which have their GUI and/or instructions in local languages for people to make use of them. This will not only make it easy for the masses to use software but will also increase computer literacy in the country. Building new software with interfaces in various local languages is one of ways to achieve this. But, to understand and modify existing free software available under GNU GPLv3 and similar licenses and port them into local languages is perhaps the best and the easiest way. The main advantage of this approach is that we already have very good quality software available for English which has been tested and changed to make it the perfect one. So instead of developing a new software right from scratch it is easier to modify this available software to provide Indic language support.

With this approach in mind, we have selected the most widely used applications in the GNU/Linux environment which is the \textit{GNOME-terminal} and \textit{vim-editor}. There is very little support for local languages in the \textit{GNOME-terminal}. Languages like the Devanagari script (Hindi and Marathi) have almost no support. Our aim is to make the \textit{GNOME-terminal} available for people who know the Devanagari script.

The successful implementation of Devanagari script rendering in \textit{GNOME-terminal} will help the developers from other language communities to implement support for their language also. 
\end{abstract}

%_____________________________________________________________________________________________ 
